Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)

### 2018-11-01 GSV-comment-brief.Rmd
Many updates

---
title: "Lies, versus the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
bibliography: bibliography.bib
link-citations: yes
editor_options: 
  chunk_output_type: console
---

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of liars in "coin flip" style experiments. However, their method appears 
>  to give erroneous confidence intervals. I explain why and describe two better
>  ways to calculate probability distributions.

Some people are honest, while others will lie whenever it benefits them. We would like to know the
prevalence of lying, since a society where many people lie is likely to experience
economic and social problems. Since we cannot simply ask people if they are liars, one way to
estimate the proportion of liars in a group is to ask them to report the result of a coin flip or
other random device, offering them a payment if they report heads. Liars don't always lie: they 
only lie when it benefits them. So they always report heads irrespective of the true coin flip.
^[@Garbarino2018 maintain this assumption and so shall I.] If there are many more heads than
we would expect by chance, we can assume many people are lying. But how many?

@Garbarino2018 -- GSV from here on -- introduce an alternative method. They claim that their method 
corrects for this problem and can estimate the full distribution of
lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power 
calculations.

@@

nreps <- 1000L
rewrite_csv <- FALSE # set to TRUE to (re)create the simulations CSV file
cache_results <- TRUE # FALSE to recalculate all results. TRUE for speed.
sample_from_pop <- TRUE # if TRUE, the number of liars in the sample is randomly drawn 
                        # from a population with `Liars` liars. 
                        # If FALSE it is fixed at `Liars * N`.
estimate_lies_not_liars <- FALSE # if FALSE, use Liars/N as ground truth
                                # if TRUE, use (R-heads)/(N-heads)
```

@@

true_data <- tidyr::crossing(
  N     = params$N,
  Liars = params$Liars,
  P     = params$P
)
true_data$Liars <- round(true_data$Liars * true_data$N, 0)

simulate_cointoss <- function (row) {
  h_liars <- rbinom(1, row["Liars"], 1 - row["P"])
  h_honest <- rbinom(1, row["N"] - row["Liars"], 1 - row["P"])
  R <- row["Liars"] + h_honest
  heads <- h_honest + h_liars
  c(R, heads)
}

results <- replicate(nreps, apply(true_data, 1, simulate_cointoss))

results_R <- results[1, , ]
results_heads <- results[2, , ]
colnames(results_R) <- paste0("R", 1:nreps)
colnames(results_heads) <- paste0("heads", 1:nreps)

sim_data <- true_data %>% 
      cbind(as_tibble(results_R)) %>% 
      cbind(as_tibble(results_heads)) %>% 
      gather("stat", "result", starts_with("R"), starts_with("heads")) %>%
      extract(stat, c("stat", "sim"), regex="(.*?)(\\d+)", convert = TRUE) %>%
      spread(stat, result) %>%  
      arrange(N, Liars, P)

@@

if (rewrite_csv) {
  readr::write_csv(sim_output, path = "sim-output.csv")

  # the java only lets you select a document from your home directory
  copied_to_home_dir_ok <- file.copy("sim-output.csv", normalizePath("~"), overwrite = TRUE)
  stopifnot(copied_to_home_dir_ok)
  # now run java -jar LyingCalculator.jar from the LyingCalculator directory
}
```

@@

sim_est <- left_join(sim_data, gsv_estimates, by = c("N", "R", "P", "CI"))

@@

prop_liars_ev_gsv <- function(heads, N, P) {
  dist_L <- dist_L_gsv(heads, N, P)
  prop_lied <- prop_liars(0:heads, heads, N)
  sum(dist_L * prop_lied)
}

@@

# reshape to long by method
sim_est %<>%
      tidyr::gather(measure, value, contains(".")) %>% 
      tidyr::extract(measure, into = c("statistic", "method"), regex = "(LB|EV|UB)\\.(.*)") %>% 
      tidyr::spread(statistic, value)

# alternative "ground truth" is proportion of lies: (R - heads)/(N - heads)
if (estimate_lies_not_liars) {
  sim_est %<>% mutate(
          true_prop = (R - heads)/(N - heads)
        )
} else {
  sim_est %<>% mutate(
          true_prop = Liars/N
        )
}

@@

I ran simulations to check the overall performance of the GSV confidence intervals. 
For each simulation and confidence interval, I computed whether the confidence interval 
contained the true value. Table \@ref(tab:coverage-overall) shows the results.

@@

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. GSV
intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
this problem holds across all simulated probabilities of the low outcome $P$, confidence
levels, and sample sizes $N$ (up to 500).^[In the appendix.]

Why does this happen? We can get a clue by running the GSV method when there are 10 reports of 
"heads" out of 10 for a fair coin flip ($R = N = 10, P = 0.5$). The resulting point estimate is that
100% of subjects lied. The upper and lower confidence intervals are also 100%. Really? Can we rule out
that 8 subjects lied, and the two honest subjects both saw heads?

The GSV method works like this. First, given $R$ reports of heads, the probability that a total 
of $T$ heads was observed is calculated as:

@@

There are two problems with this approach.

First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there
are probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
The probability distribution above does not take account of this. In particular, for $R=N$, 
the equation above reduces to the binomial distribution.

Second, suppose $R = 10$ heads out of 10 are reported, and suppose 9 heads were really observed, $T
= 9$. The proportion of people who actually lied in the sample is indeed 100%. But it is 100% of 1
person -- the only person who saw tails. As an estimate of the proportion of liars in the sample --
i.e. the proportion who would have lied, had they seen tails -- that is very noisy.^[The
true number of liars in the sample is unobserved, and needs to be estimated, even if we are not trying
to make inferences to a larger population.]  The GSV method treats it as certain. In other words, GSV estimates the proportion of lies, rather than the proportion of lying 
liars who tell them. But the latter is the statistic we care about.

@@

* With probability $\frac{1}{2^{10}}$, there were really $T = 10$ heads. Nobody lied in the sample,
but the proportion of people who lied *out of those who could*, $\frac{R-T}{N-T}$, is undefined because
nobody got the chance to lie.^[The GSV software seems to resolve this by fixing the proportion of 
lies to 100%.]

@@

@@

The same problem happens in less extreme form whenever $R$ is high relative to $N$. Table 
\@ref(tab:coverage-rn) shows this by splitting the simulations by $R/N$. When $R/N$ is
less than 0.5, coverage levels are OK. When it is greater than 0.5, they are not. Note that
for fair coin flips, $R/N$ is typically greater than 0.5, in the simulations and in reality.^[
If we disaggregate by $N$, $P$, and $R/N$, 95% confidence intervals achieve their nominal 
coverage level in only `r round(prop_ok*100, 1)`% of cases.]

```{r coverage-rn}
coverage_rn <- sim_est %>% 
      filter(method=="gsv") %>% 
      group_by(
        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/2, 1)), labels = c("< 0.5", "&ge; 0.5"))      
      ) %>% 
      mutate(pct_cases = n()/nrow(.)) %>% 
      group_by(`R/N:`, CI) %>% 
      summarize(
        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
        `Pct cases` = pct_cases[1]
      ) %>% 
      mutate(CI = paste0("CI ", CI, "%")) %>% 
      spread(CI, mean_in_ci)

@@

One can then calculate the proportions of liars as $L/N$. Note that we are now directly estimating
how many liars are in the whole sample $N$, where a liar is someone who always reports heads. From
this, one can derive confidence intervals and expected values in the usual way.^[R code to
run these calculations is available at https://github.com/hughjonesd/GSV-comment.]

@@

Results are shown in Table \@ref(tab:coverage-allmethods). Both
frequentist and  Bayesian methods mostly achieve the nominal confidence level, with
more than 90/95/99% of intervals containing the true value. The exception is the frequentist
99% confidence interval, which is too narrow.

@@

We can also compare the accuracy of point estimates of the proportion of liars. Table
\@ref(tab:point-estimates) shows the mean squared error for methods by different $N$. For low $N$,
the best method is Bayesian and the worst is Frequentist, with GSV in between. When $N$ gets large all
methods give about the same estimates and are equally accurate.

@@

distribs <- apply(nats[, c("heads", "N")], 1, function (r) {
  N <- r["N"]
  update_prior(
      heads = r["heads"],
      N = N,
      P = 0.5, 
      prior = dbinom(0:N, N, p = pooled_prop_liars)
  )
})
names(distribs) <- nats$resnat

@@

Results are shown in Figure \@ref(fig:hj2016-pic), with means and 95% confidence intervals. There
is substantial shrinkage from the "naive" per-country estimates (using $2R/N - 1$). One of the strengths of empirical Bayes,  as @casella1985introduction points out, is that it "anticipates
regression to the mean". In other words, if we start from the prior that everyone is the same,
we will end up believing that the British are less honest, and the Chinese people are more honest,
than the experimental data *per se* suggest.

@@

prob_country_less <- function (ctry1, ctry2) {
  stopifnot(ctry1 %in% nats$resnat, ctry2 %in% nats$resnat)

  prob_first_less <- 0
  N_1 <- nats$N[nats$resnat == ctry1]
  N_2 <- nats$N[nats$resnat == ctry2]
  for (L_1 in seq(0, length.out = length(distribs[[ctry1]]))) {
    for (L_2 in seq(0, length.out = length(distribs[[ctry2]]))) {
      l_1 <- L_1/N_1
      l_2 <- L_2/N_2
      if (l_1 < l_2) {
        prob_first_less <- prob_first_less + 
            (distribs[[ctry1]][L_1 + 1] * distribs[[ctry2]][L_2 + 1])
      }
    }
  }

  return(prob_first_less)
}

@@

@@

1. Do not use the GSV confidence intervals.
2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests.
3. If your N is too small for point 2 to apply, it may be too small, full stop.
4. If increasing your N is not possible for whatever reason, consider using Bayesian methods to find
  confidence intervals and point estimates. To estimate differences between subgroups, consider
  empirical Bayes with a prior derived from the pooled sample.

@@

## Methods

Simulations parameters are shown in Table \@ref(tab:params-table).

huxtable(
        Parameter = c(
          "Sample size (N)", 
          "Proportion of liars (R/N)", 
          "Probability of bad outcome (P)"
        ),
        Values    = c(
          paste(params$N, collapse = ", "),
          paste(params$Liars, collapse = ", "),
          paste(params$P, collapse = ", ")
        ),
        add_colnames = TRUE
      ) %>% 
      set_caption("(#tab:params-table) Parameter values") %>% 
      theme_article()
```

For each parameter combination, I ran 1000 simulations. All liars always reported heads. Non-liars
reported tails with probability $P$ and heads otherwise.

## More results

@@

ggplot(coverage_grp_gsv, aes(Liars/N, mean_in_ci, colour = P)) +
      geom_point() + geom_line() + 
      geom_hline(aes(yintercept = ci/100), linetype = 2) +
      facet_grid(N ~ CI, labeller = "label_both") +
      xlab("True proportion of liars L/N") + ylab("Proportion within C.I.")

>>>>

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
bibliography: bibliography.bib
link-citations: yes
---

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of liars in "coin flip" style experiments. However, their method appears 
>  to give erroneous confidence intervals. I explain why, and describe two better
>  ways to calculate probability distributions.

@@

nreps <- 1000L

# set to FALSE to recalculate all results; TRUE for speed:
cache_results <- FALSE

# set to TRUE to (re)create the simulations CSV file:
rewrite_csv <- FALSE

# if TRUE, the number of liars in each simulation is randomly drawn
# from a population with `Liars` liars.
# If FALSE, the number of liars is fixed at `Liars * N`.
# If you change this, you may need to recreate the simulations CSV file
sample_from_pop <- FALSE

# if FALSE, use L/N as ground truth;
# if TRUE, use (R-heads)/(N-heads):
estimate_lies_not_liars <- FALSE

if (sample_from_pop && estimate_lies_not_liars) {
  stop("Can't estimate proportion of actual lies in population!")
}

params <-   list(
  N     = c(10, 50, 100, 500),
  Liars = seq(0, 1, 0.1),
  P     = c(.2, .5, .8)
)

ci_levels <- c(90L, 95L, 99L)

method_used_statement <- paste0("This paper can be recreated from the .Rmd file using different ",
      "methods to calculate confidence interval coverage and squared errors. 'Ground ",
      "truth' can be the population proportion of liars, the sample proportion of liars or ",
      "the sample proportion of actual lies. Ground truth for the document you are reading was: ",
        if (sample_from_pop) "the population proportion of liars." else 
        if (estimate_lies_not_liars) "the sample proportion of actual lies." else 
        "the sample proportion of liars."
      )

if (! sample_from_pop && ! estimate_lies_not_liars) method_used_statement <- ""

**`r method_used_statement`**

Some people are honest, while others will lie whenever it benefits them. We would like to understand
the prevalence of lying, because dishonesty may be economically and socially harmful. Since we
cannot simply ask people if they are liars, one way to estimate the proportion of liars in a group
is to ask them to report the result of a coin flip or other random device, offering them a payment
if they report heads. Liars don't always lie: they only lie when it benefits them. So they always
report heads irrespective of the true coin flip. ^[GSV maintain this assumption and so shall I.] If
there are many more heads than we would expect by chance, we can assume many people are lying. But
how many?

@Garbarino2018 -- GSV from here on -- point out this problem and introduce an alternative method.
They claim that their method corrects for this problem and can estimate the full distribution of
lying outcomes, and they recommend using it for confidence intervals, hypothesis testing and power
calculations.

@@

sim_data <- tidyr::crossing(
  N     = params$N,
  Liars = params$Liars,
  P     = params$P
)
sim_data$Liars_pop_pct <- sim_data$Liars

sim_data <- sim_data[rep(1:nrow(sim_data), each = nreps), ]
sim_data$sim <- rep_len(1:nreps, nrow(sim_data))

if (sample_from_pop) {
  sim_data %<>% 
        group_by(N, Liars, P) %>% 
        mutate(
          Liars_sample = rbinom(n(), N, Liars)
        ) %>% 
        ungroup() %>% 
        mutate(
          Liars = Liars_sample,
          Liars_sample = NULL
        )
} else { 
  sim_data$Liars <- round(sim_data$Liars * sim_data$N, 0)
}

simulate_cointoss <- function (row) {
  h_liars <- rbinom(1, row["Liars"], 1 - row["P"])
  h_honest <- rbinom(1, row["N"] - row["Liars"], 1 - row["P"])
  R <- row["Liars"] + h_honest
  names(R) <- NULL
  heads <- h_honest + h_liars
  c(R = R, heads = heads)
}

results <- apply(sim_data, 1, simulate_cointoss)

sim_data$R <- results["R", ]
sim_data$heads <- results["heads",]

sim_data <- sim_data %>% arrange(N, Liars, P)

@@

if (rewrite_csv) {
  path <- paste0("GSV-sims", if (sample_from_pop) "-pop-sample", ".csv")

  readr::write_csv(sim_output, path = path)

  # the java only lets you select a document from your home directory
  copied_to_home_dir_ok <- file.copy(path, normalizePath("~"), overwrite = TRUE)
  stopifnot(copied_to_home_dir_ok)
  # now run java -jar LyingCalculator.jar from the LyingCalculator directory
  # make sure the old output file (xxxOutput.csv) is deleted first, or it will be appended to!
}

sim_est <- sim_data
```

@@

sim_est <- left_join(sim_est, gsv_estimates, by = c("N", "R", "P", "CI"))

@@

prop_liars_ev_gsv <- function(heads, N, P) {
  dist_L <- dist_L_gsv(heads, N, P)
  prop_lied <- prop_liars(0:heads, heads, N)
  sum(dist_L * prop_lied)
}
```

```{r check-gsv-posterior, eval = FALSE}

# if we assume that liars are not uniformly distributed, the posterior of number of heads
# is not like the prior
N <- 10
CI <- 0.9
tmp <- replicate(10000, {
  # L <- sample(1:N, 1) # for this, always accurate?
  L <- rbinom(1, N, 0.1) # not many liars
  HL <- rbinom(1, L, 0.5)
  HNL <- rbinom(1, N-L, 0.5)
  R <- L + HNL
  H <- HL + HNL
  c(L, R, H, N, CI, prop_liars_ci_gsv(CI, R, N, 0.5))
})

tmp <- as.data.frame(t(tmp))
names(tmp) <- c('L', 'R', 'H', 'N', 'CI', 'cilo', 'cihi')
tmp$lies_told <- with(tmp, (R-H)/(N-H))
tmp$lies_in_ci <- tmp$cilo <= tmp$lies_told & tmp$lies_told <= tmp$cihi

# the prior:
ggplot(tmp, aes(H)) + geom_bar(aes(y = calc(prop))) + 
  geom_line(data = tmp[tmp$R > quantile(tmp$R, 0.8), ], aes(H, calc(prop)))
# the posterior is not the prior:
hist(tmp$H, col = "grey", breaks = 0:N, freq = FALSE, ylim = c(0, 1))
hist(tmp$H[tmp$R==10], breaks = 0:N, add= T, freq = FALSE, col = rgb(1,0,0,.5))

# the posterior:
lines(density(with(tmp, H[R > quantile(R, 0.9)])))

# how accurate are we for different numbers of R.
# NB you can also judge accuracy by different numbers of H, but I'm not sure that's fair as H is
# an unknown parameter - maybe it is like saying "confidence interval coverage is way off when
# the errors are big!"

GSV_coverage <- tmp %>% group_by(R) %>% 
  summarize(n_sims = n(), coverage = mean(lies_in_ci))

tmp %<>% left_join(GSV_coverage, by = "R")

scale_fac <- max(tmp$n_sims)
ggplot(GSV_coverage, aes(R)) + 
    geom_hline(yintercept = CI, linetype = 2) +
    geom_line(aes(y = coverage), colour = "red") +
    geom_line(aes(y = n_sims/scale_fac), colour = "grey") +
    scale_y_continuous(sec.axis = sec_axis(~.*scale_fac, name = "N sims"))

plot(GSV_coverage$R, GSV_coverage$coverage, type = "l")
# number of cases:
points(GSV_coverage$R, GSV_coverage$n_sims/max(GSV_coverage$n_sims), type = "h", col = "grey")

table(low_coverage = tmp$coverage < 0.8, tmp$R > 60) %>% prop.table(2)
```

@@

# reshape to long by method
sim_est %<>%
      tidyr::gather(measure, value, matches("^(LB|EV|UB)\\.")) %>% 
      tidyr::extract(measure, into = c("statistic", "method"), regex = "^(LB|EV|UB)\\.(.*)") %>% 
      tidyr::spread(statistic, value)

# alternative "ground truths":
if (estimate_lies_not_liars) {
  sim_est %<>% mutate(
          true_prop = (R - heads)/(N - heads)
        )
} else if (sample_from_pop) {
  sim_est %<>% mutate(
          true_prop = Liars_pop_pct
        )
} else {
  sim_est %<>% mutate(
          true_prop = Liars/N
        )
}

@@

I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
parameters are shown in Table \@ref(tab:params-table). For each parameter combination, I ran 1000
simulations. "Liars" always reported heads. Non-liars reported tails with probability $P$ and
heads otherwise.

huxtable(
        Parameter = c(
          "Sample size (N)", 
          "Proportion of liars (L/N)", 
          "Probability of bad random outcome (P)"
        ),
        Values    = c(
          paste(params$N, collapse = ", "),
          paste(params$Liars, collapse = ", "),
          paste(params$P, collapse = ", ")
        ),
        add_colnames = TRUE
      ) %>% 
      set_caption("(#tab:params-table) Parameter values") %>% 
      theme_article()
```

For each simulation and confidence interval, I computed whether the confidence interval 
contained the true value of $L/N$. Table \@ref(tab:coverage-overall) shows the results.

@@

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This
is called "achieving nominal coverage". GSV
intervals are far from this. The confidence intervals are too narrow. Further analysis shows that
this problem holds across all simulated probabilities of the low outcome $P$, confidence
levels, and sample sizes $N$ (up to 500).^[In the appendix.]

Why does this happen? We can get a clue by running the GSV method when there are 10 reports of 
"heads" out of 10 for a fair coin flip ($R = N = 10, P = 0.5$). The resulting point estimate is that
100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this might
seem wrong. Can we rule out that 8 subjects lied, and the two honest subjects both saw heads?

In fact, the GSV method works like this. First, given $R$ reports of heads, the probability that a total 
of $T$ "true" heads were observed is calculated as:

@@

@@

* With probability $\frac{1}{1024}$, there were really $T = 10$ heads. Nobody lied in the sample.^[But  the proportion of people who lied *out of those who saw tails* is undefined, because noone saw tails. The 
GSV software seems to resolve this by fixing the proportion of lies to 100%.]

@@

There are two problems with this approach. One is statistical, one is conceptual.

First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there
are probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
The probability distribution above does not take account of this. In particular, for $R=N$, 
the equation above reduces to the binomial distribution. This is not correct.

Second, more importantly, the GSV approach estimates the distribution of the proportion of 
*lies actually told*, among the subsample of people who saw tails:

\[
\textit{Lies} = \frac{R-T}{N-T} 
\]

But usually, we are not interested in the proportion of
lies actually told. We care about how many people in the sample *are liars*, who would lie if they
saw tails:

\[
\textit{Liars} = \frac{L}{N}.
\]

Suppose $R = 10$ heads out of 10 are reported, and suppose 9 heads were really observed, $T = 9$.
$\textit{Lies}$ is indeed 100%.  But it is 100% of 1 person
-- the only person who saw tails. That one person's behaviour is an unbiased estimate of the
proportion of liars in the sample, $\textit{Liars}$. But it is a very noisy estimate.

The first problem means that when $R$ is very high or low,
the percentage of confidence intervals containing $\textit{Lies}$
may fall off sharply.^[Depending on the distribution of the number of liars $L$.]

The second problem means that the percentage of confidence intervals containing $\textit{Liars}$
is almost always much less than the nominal coverage.

@@

The problem is especially bad when there are many reports of heads. In this case there were probably
many true heads, so $T$ is high and the true sample size $N-T$ is low. Table \@ref(tab:coverage-rn)
shows this. It splits the simulations by the proportion of reported heads, $R/N$. Coverage levels
fall off sharply as $R/N$ increases. Note that for fair coin flips, $R/N$ is typically greater than
0.5, in the simulations and in reality.

```{r coverage-rn}
coverage_rn <- sim_est %>% 
      filter(method=="gsv") %>% 
      group_by(
        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/4, 1/2, 3/4, 1)))      
      ) %>% 
      mutate(pct_cases = n()/nrow(.)) %>% 
      group_by(`R/N:`, CI) %>% 
      summarize(
        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
        `Pct cases` = pct_cases[1]
      ) %>% 
      mutate(CI = paste0("CI ", CI, "%")) %>% 
      spread(CI, mean_in_ci)

@@

One can then estimate the proportion of $\textit{Liars}$ as $L/N$. From
this, one can derive confidence intervals and expected values in the usual way.^[R code to
run these calculations, along with all the code for this article, is available at https://github.com/hughjonesd/GSV-comment .]

@@

Results are shown in Table \@ref(tab:coverage-allmethods). Both frequentist and  Bayesian methods
mostly achieve the nominal confidence level, with more than 90/95/99% of intervals containing the
true value of $Liars$. The exception is the frequentist 99% confidence interval, which is too
narrow.

@@

We can also compare the accuracy of point estimates of $\textit{Liars}$. Table
\@ref(tab:point-estimates) shows the mean squared error for methods by different $N$. For low $N$,
the best method is Bayesian and the worst is Frequentist, with GSV in between. When $N$ gets large all
methods give about the same estimates and are equally accurate.

@@

distribs <- apply(nats[, c("heads", "N")], 1, function (r) {
  N <- r["N"]
  update_prior(
      heads = r["heads"],
      N = N,
      P = 0.5, 
      prior = dbinom(0:N, N, p = pooled_prop_liars)
  )
})

names(distribs) <- nats$resnat

@@

Results are shown in Figure \@ref(fig:hj2016-pic), with means and 95% confidence intervals. There
is substantial shrinkage from the "naive" per-country estimates (using $2R/N - 1$). One of the strengths of empirical Bayes,  as @casella1985introduction points out, is that it "anticipates
regression to the mean". In other words, if we start from the prior that everyone is the same,
we will end up believing that the British people in the sample are less honest, and the Chinese 
people more honest, than the experimental data *per se* suggest.

@@

prob_country_less <- function (ctry1, ctry2) {
  stopifnot(ctry1 %in% nats$resnat, ctry2 %in% nats$resnat)
  N_1 <- nats$N[nats$resnat == ctry1]
  N_2 <- nats$N[nats$resnat == ctry2]
  heads_1 <- nats$heads[nats$resnat == ctry1]
  heads_2 <- nats$heads[nats$resnat == ctry2]  
  diff_dist <- compare_groups(heads1 = heads_1, N1 = N_1, heads2 = heads_2, N2 = N_2, P = 0.5)

  prob_first_less <-sum(diff_dist$prob[diff_dist$diff < 0]) 
  return(prob_first_less)
}

@@

# The population

So far we have been trying to estimate the proportion of $\textit{Liars}$ in the sample. In fact,
we usually care about the proportion in liars in populations from which the sample is drawn. This
adds another layer of randomness. When $N$ is large, the sample distribution should approximate
the population distribution and either frequentist or Bayesian approaches should work. Further
simulations, not shown, suggest that Bayesian confidence intervals are less robust in bounding
$Liars$ in the population from which the sample $L$ is randomly drawn.

@@

1. Do not use the GSV confidence intervals, unless you are specifically interested in *Lies* rather
  than *Liars*. Even in that case be aware that the confidence intervals have low coverage for extreme
  values of $R$.
2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests. If you are interested in the population from which the sample is drawn,
  you should do so, as they are most robust.
3. If your N is small and you are interested in the sample proportion of $\textit{Liars}$, consider
  Bayesian estimates. To estimate differences between subgroups, consider
  empirical Bayes with a prior derived from the pooled sample.

Lastly, here is a simple way to avoid these shenanigans. Ask a group of $N$ experimental subjects, 
not to flip a coin, but to draw a black or white ball, without replacement, from an urn containing 
$N$ balls, of which $T$ are white. Pay them if they report a white ball. You will then know that the 
proportion of lies told is $(R-T)/(N-T)$, and this will also be the proportion of liars, in a sample
of $N-T$ subjects. So you can estimate the proportion of $\textit{Lies}$, and of the lying 
$\textit{Liars}$ who tell them.

@@

R code to reproduce this comment is available at https://github.com/hughjonesd/GSV-comment . You
can also rerun the simulations to test confidence interval coverage of $Lies$, of $Liars$, or
of $Liars$ in a population from which samples are drawn. Lastly, I provide code to find Bayesian
posterior distributions of $Liars$.

@@

g <- ggplot(coverage_grp_gsv, aes(Liars/N, mean_in_ci, colour = P)) +
      geom_hline(aes(yintercept = ci/100), linetype = 2) +
      facet_grid(N ~ CI, labeller = "label_both") +
      xlab("True proportion of liars L/N") + ylab("Proportion within C.I.")

if (sample_from_pop) g + geom_smooth(method = "loess") else g + geom_point() + geom_line()
